New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/weakschur.tex
tableaux 5

\renewcommand{\arraystretch}{2}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
\cline{4-9}
   \multicolumn{5}{c|}{} & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
\hline
   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
\hline
\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
\hline
...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
\hline
\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
\hline
...&...&...&...&...&...&...&...&...&...&...&...&...\\
\hline
\end{tabular}

\textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b

We denote by \(g\) the projection of the equivalence relation induced by the partition of \([\![1,q]\!]\) and \(h\) the
one induced by the partition of \([\![1,p]\!]\). Each equivalence class is represented by a single integer, therefore :
\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
\]
\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
\Longrightarrow h(x+y) \neq h(x)
\]

Let \( f : [\![1,b+p \time a]\!] \longrightarrow [\![1,n]\!] \) such as:
\\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
\\\\-if \( x \in [\![1,b+p \time a]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
\\\\-if \( x \in [\![1,b+p \time a]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{L}): f(x)=n-1+h(\lambda(x))\)
\\\\
f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+p \time a]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)

>>>>

\renewcommand{\arraystretch}{2}
\begin{center}
\[
\begin{array}{|c|c|c|c|c|c|c|c|c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{blue}}c|>{\columncolor{green}} c|}
\cline{6-9}
   \multicolumn{5}{c|}{} & \cellcolor{green}1 & \cellcolor{green}2 & \cellcolor{blue} 3&\cellcolor{green}4&5&6&7&8 \\
\hline
   \cellcolor{red}9 & \cellcolor{red}10 & \cellcolor{red}11 & \cellcolor{red}12 &\cellcolor{red}13&\cellcolor{red}14&\cellcolor{red}15&\cellcolor{red}16&\cellcolor{red}17&18&19&20&21\\
\hline
\cellcolor{yellow}22&\cellcolor{yellow}23&\cellcolor{yellow}24&\cellcolor{yellow}25&\cellcolor{yellow}26&\cellcolor{yellow}27&\cellcolor{yellow}28&\cellcolor{yellow}29&\cellcolor{yellow}30&31&32&33&34\\
\hline
...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...\cellcolor{yellow}&...&...&...&...\\
\hline
\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&\cellcolor{red}...&...&...&...&...\\
\hline
...&...&...&...&...&...&...&...&...&...&...&...&...\\
\hline
\end{array}
\]
\end{center}
\textsc{Proof :}Let \((q,n,b) \in (\mathbb{N}^*)^3\), let \( (p,k) \in (\mathbb{N}^*)^2\), let a=q-b. \\
We denote by \(g\) the projection of the equivalence relation induced by the partition of \([\![1,q]\!]\) and \(h\) the
one induced by the partition of \([\![1,p]\!]\). Each equivalence class is represented by a single integer, therefore :
\[ g : [\![1,q]\!] \longrightarrow [\![1,n]\!] \text{ and } (A_{g^{-1}(1)},...A_{g^{-1}(q)})\text{ is a b-WSF-template.}
\]
\[h : [\![1,p]\!] \longrightarrow [\![1,k]\!] \text{ and } \forall (x,y) \in [\![1,q]\!]^2 \text{, } h(x) = h(y)
\Longrightarrow h(x+y) \neq h(x)
\]

Let \( f : [\![1,b+pa]\!] \longrightarrow [\![1,n]\!] \) such as:
\\\\-if x \(\leqslant b \text{ (we will note x} \in \mathcal{T}): f(x)=g(x)\)
\\\\-if \( x \in [\![1,b+pa]\!] \text{ and } \pi(x) \notin A_n \text{ (we will note x} \in \mathcal{C}): f(x)=g(\pi(x))\)
\\\\-if \( x \in [\![1,b+pa]\!]  \text{ and }\pi(x) \in A_n \text{ (we will note x} \in \mathcal{L}): f(x)=n-1+h(\lambda(x))\)
\\\\
f is well defined because \(\pi\) is defined for x\(>b\) and \(\forall x \in \![1,b+pa]\!], f(x)\leqslant n+k-1\) because h(\(\lambda(x))\leqslant k\)
